Market simulator

### 2020-10-05 analysis/05_market_simulator.Rmd
Added references for organization and persona defaults using imported data, removed the superfluous first column, and updated indexing

```{r organization-reactive-table}
# Placeholder for organization reactive table
org_table <- as.data.frame(matrix(0, nrow = nrow(organization_data)))

# Assign level labels
org_table$levels = c(
  # Organization
  "Amnesty International",
  "Greenpeace", 
  "Oxfam", 
  "Red Cross",
  # Issue area
  "Environment", 
  "Human rights",
  "Refugee relief",
  # Financial transparency
  "Engages in financial transparency",
  # Financial accountability
  "Engages in financial accountability",
  # Funding sources
  "Handful of wealthy private donors", 
  "Government grants",
  # Relationship with host government
  "Criticized by government",
  "Under government crackdown"
)

@@

```{r persona-reactive-table}
# Placeholder for persona reactive table
per_table <- as.data.frame(matrix(0, nrow = nrow(persona_data)))

# Assign covariate labels
per_table$levels <- c(
  # Intercept
  "Intercept",
  # Follow national news
  "Once a week",
  "At least once a day",
  # Follow international news
  "Sometimes",
  "Always",
  # Mediums to follow news
  "TV",
  "Print",
  "Online (not social media)",
  "Social media",
  "Radio",
  "Email newsletter",
  "News app",
  # Follow government and public affairs
  "Often", 
  # Traveled to a developing country
  "Traveled to a developing country", 
  # Liberal to Conservative
  "Somewhat liberal",
  "Slightly liberal",
  "Moderate",
  "Slightly conservative",
  "Somewhat conservative",
  "Extremely conservative",
  # Trust in political institutions
  "Very little trust in political institutions",
  "Little trust in political institutions",
  "Neutral trust in political institutions",
  "Some trust in political institutions",
  "A lot of trust in political institutions",
  "Complete trust in political institutions",
  # People should be more charitable
  "Disagree",
  "Somewhat disagree",
  "Neutral",
  "Somewhat agree",
  "Agree",
  "Strongly agree",
  # Religious attendance
  "Rarely attend",
  "Attend at least once a month",
  # Importance of religion
  "Important",
  # Religion
  "Protestant",
  "Christian Orthodox",
  "Jewish",
  "Muslim",
  "Sikh",
  "Hindu",
  "Buddhist",
  "Atheist",
  "Other religion",
  # Importance of trusting charities
  "Very unimportant",
  "Somewhat unimportant",
  "Neutral importance",
  "Somewhat important",
  "Very important",
  "Essential",
  # Trust in charities
  "Very little trust in charities",
  "Little trust in charities",
  "Neutral trust in charities",
  "Some trust in charities",
  "A lot of trust in charities",
  "Complete trust in charities",
  # Donation frequency
  "Donate at least once a month", 
  # Donated last year
  "$50-$99",
  "$100-$499",
  "$500-$999",
  "$1,000-$4,999",
  "$5,000-$9,999",
  "$10,000+",
  # Volunteered in past 12 months
  "Volunteered in past 12 months",
  # Volunteer frequency
  "Rarely volunteer",
  "Volunteer more than once a month, less than once a year",
  "Volunteer at least once a month",
  # History of activism
  "Personally involved",
  # History of family activism
  "Family involved",
  # Church or religious organization
  "Inactive church member",
  "Active church member",
  # Sport or recreational organization
  "Inactive sports or rec organization member",
  "Active sports or rec organization member", 
  # Art, music, or educational organization
  "Inactive art, music, or educational organization member",
  "Active art, music, or educational organization member",
  # Labor union
  "Inactive union member",
  "Active union member",
  # Political party
  "Inactive political party member",
  "Active political party member",
  # Environmental organization
  "Inactive environmental organization member",
  "Active environmental organization member",
  # Professional association
  "Inactive professional association member",
  "Active professional association member",
  # Humanitarian or charitable organization
  "Inactive humanitarian or charitable organization member",
  "Active humanitarian or charitable organization member",
  # Consumer organization
  "Inactive consumer organization member",
  "Active consumer organization member",
  # Other organization
  "Inactive member in another organization",
  "Active member in another organization",
  # Gender
  "Female",
  "Transgender",
  "Prefer not to say",
  "Other gender",
  # Marital status
  "Widowed",
  "Divorced",
  "Separated",
  "Never married",
  # Education
  "High school graduate", 
  "Some college",
  "2 year degree",
  "4 year degree",
  "Graduate or professional degree",
  "Doctorate",
  # Income
  "More than median of $61,372", 
  # Race
  "White", 
  "Black or African American", 
  "American Indian or Alaskan Native", 
  "Asian", 
  "Native Hawaiian or Pacific Islander",
  "Other race",
  # Age
  "More than median age of 36"
)

@@

  # Persona 1 predicted betas
  per1_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,3])

  # Persona 1 expected utilities
  per1_org1_exp <- exp(t(org_choice[,3]) %*% as.matrix(per1_betas))
  per1_org2_exp <- exp(t(org_choice[,4]) %*% as.matrix(per1_betas))
  per1_org3_exp <- exp(t(org_choice[,5]) %*% as.matrix(per1_betas))
  per1_org4_exp <- exp(t(org_choice[,6]) %*% as.matrix(per1_betas))

@@

  # Persona 2 predicted betas
  per2_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,4])

  # Persona 2 expected utilities
  per2_org1_exp <- exp(t(org_choice[,3]) %*% as.matrix(per2_betas))
  per2_org2_exp <- exp(t(org_choice[,4]) %*% as.matrix(per2_betas))
  per2_org3_exp <- exp(t(org_choice[,5]) %*% as.matrix(per2_betas))
  per2_org4_exp <- exp(t(org_choice[,6]) %*% as.matrix(per2_betas))

@@

  # Persona 3 predicted betas
  per3_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,5])

  # Persona 3 expected utilities
  per3_org1_exp <- exp(t(org_choice[,3]) %*% as.matrix(per3_betas))
  per3_org2_exp <- exp(t(org_choice[,4]) %*% as.matrix(per3_betas))
  per3_org3_exp <- exp(t(org_choice[,5]) %*% as.matrix(per3_betas))
  per3_org4_exp <- exp(t(org_choice[,6]) %*% as.matrix(per3_betas))

@@

# Organization
selectInput(
  "org1_org",
  label = "Organization:",
  choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
  selected = "Red Cross",
  width = "450px"
)

# Issue area
selectInput(
  "org1_issue", 
  label = "Issue Area:",
  choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
  selected = "Emergency response",
  width = "450px"
)

@@

# Mediums to follow news
selectInput(
  "per1_news_medium",
  label = "Medium to follow news:",
  choices = c(
    "TV",
    "Print",
    "Online (not social media)",
    "Social media",
    "Radio",
    "Email newsletter",
    "News app"
  ),
  multiple = TRUE,
  selected = c("TV", "Print", "Social media"),
  width = "450px"
)

@@

downloadHandler(
  filename = function() {
    paste0("org_data_",Sys.time(),".csv")
  },
  content = function(file) {
    write.csv(org_reactive(), file)
  }
)

@@

downloadHandler(
  filename = function() {
    paste0("persona_data_",Sys.time(),".csv")
  },
  content = function(file) {
    write.csv(per_reactive(), file)
  }
)

@@

>>>>

```{r organization-reactive-table}
# Assign level labels
org_table <- data.frame(
  levels = c(
    # Organization
    "Amnesty International",
    "Greenpeace", 
    "Oxfam", 
    "Red Cross",
    # Issue area
    "Environment", 
    "Human rights",
    "Refugee relief",
    # Financial transparency
    "Engages in financial transparency",
    # Financial accountability
    "Engages in financial accountability",
    # Funding sources
    "Handful of wealthy private donors", 
    "Government grants",
    # Relationship with host government
    "Criticized by government",
    "Under government crackdown"
  )
)

@@

```{r persona-reactive-table}
# Assign covariate labels
per_table <- data.frame(
  levels = c(
    # Intercept
    "Intercept",
    # Follow national news
    "Once a week",
    "At least once a day",
    # Follow international news
    "Sometimes",
    "Always",
    # Mediums to follow news
    "TV",
    "Print",
    "Online (not social media)",
    "Social media",
    "Radio",
    "Email newsletter",
    "News app",
    # Follow government and public affairs
    "Often", 
    # Traveled to a developing country
    "Traveled to a developing country", 
    # Liberal to Conservative
    "Somewhat liberal",
    "Slightly liberal",
    "Moderate",
    "Slightly conservative",
    "Somewhat conservative",
    "Extremely conservative",
    # Trust in political institutions
    "Very little trust in political institutions",
    "Little trust in political institutions",
    "Neutral trust in political institutions",
    "Some trust in political institutions",
    "A lot of trust in political institutions",
    "Complete trust in political institutions",
    # People should be more charitable
    "Disagree",
    "Somewhat disagree",
    "Neutral",
    "Somewhat agree",
    "Agree",
    "Strongly agree",
    # Religious attendance
    "Rarely attend",
    "Attend at least once a month",
    # Importance of religion
    "Important",
    # Religion
    "Protestant",
    "Christian Orthodox",
    "Jewish",
    "Muslim",
    "Sikh",
    "Hindu",
    "Buddhist",
    "Atheist",
    "Other religion",
    # Importance of trusting charities
    "Very unimportant",
    "Somewhat unimportant",
    "Neutral importance",
    "Somewhat important",
    "Very important",
    "Essential",
    # Trust in charities
    "Very little trust in charities",
    "Little trust in charities",
    "Neutral trust in charities",
    "Some trust in charities",
    "A lot of trust in charities",
    "Complete trust in charities",
    # Donation frequency
    "Donate at least once a month", 
    # Donated last year
    "$50-$99",
    "$100-$499",
    "$500-$999",
    "$1,000-$4,999",
    "$5,000-$9,999",
    "$10,000+",
    # Volunteered in past 12 months
    "Volunteered in past 12 months",
    # Volunteer frequency
    "Rarely volunteer",
    "Volunteer more than once a month, less than once a year",
    "Volunteer at least once a month",
    # History of activism
    "Personally involved",
    # History of family activism
    "Family involved",
    # Church or religious organization
    "Inactive church member",
    "Active church member",
    # Sport or recreational organization
    "Inactive sports or rec organization member",
    "Active sports or rec organization member", 
    # Art, music, or educational organization
    "Inactive art, music, or educational organization member",
    "Active art, music, or educational organization member",
    # Labor union
    "Inactive union member",
    "Active union member",
    # Political party
    "Inactive political party member",
    "Active political party member",
    # Environmental organization
    "Inactive environmental organization member",
    "Active environmental organization member",
    # Professional association
    "Inactive professional association member",
    "Active professional association member",
    # Humanitarian or charitable organization
    "Inactive humanitarian or charitable organization member",
    "Active humanitarian or charitable organization member",
    # Consumer organization
    "Inactive consumer organization member",
    "Active consumer organization member",
    # Other organization
    "Inactive member in another organization",
    "Active member in another organization",
    # Gender
    "Female",
    "Transgender",
    "Prefer not to say",
    "Other gender",
    # Marital status
    "Widowed",
    "Divorced",
    "Separated",
    "Never married",
    # Education
    "High school graduate", 
    "Some college",
    "2 year degree",
    "4 year degree",
    "Graduate or professional degree",
    "Doctorate",
    # Income
    "More than median of $61,372", 
    # Race
    "White", 
    "Black or African American", 
    "American Indian or Alaskan Native", 
    "Asian", 
    "Native Hawaiian or Pacific Islander",
    "Other race",
    # Age
    "More than median age of 36"
  )
)

@@

  # Persona 1 predicted betas
  per1_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,2])

  # Persona 1 expected utilities
  per1_org1_exp <- exp(t(org_choice[,2]) %*% as.matrix(per1_betas))
  per1_org2_exp <- exp(t(org_choice[,3]) %*% as.matrix(per1_betas))
  per1_org3_exp <- exp(t(org_choice[,4]) %*% as.matrix(per1_betas))
  per1_org4_exp <- exp(t(org_choice[,5]) %*% as.matrix(per1_betas))

@@

  # Persona 2 predicted betas
  per2_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,3])

  # Persona 2 expected utilities
  per2_org1_exp <- exp(t(org_choice[,2]) %*% as.matrix(per2_betas))
  per2_org2_exp <- exp(t(org_choice[,3]) %*% as.matrix(per2_betas))
  per2_org3_exp <- exp(t(org_choice[,4]) %*% as.matrix(per2_betas))
  per2_org4_exp <- exp(t(org_choice[,5]) %*% as.matrix(per2_betas))

@@

  # Persona 3 predicted betas
  per3_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,4])

  # Persona 3 expected utilities
  per3_org1_exp <- exp(t(org_choice[,2]) %*% as.matrix(per3_betas))
  per3_org2_exp <- exp(t(org_choice[,3]) %*% as.matrix(per3_betas))
  per3_org3_exp <- exp(t(org_choice[,4]) %*% as.matrix(per3_betas))
  per3_org4_exp <- exp(t(org_choice[,5]) %*% as.matrix(per3_betas))

@@

# Organization
selectInput(
  "org1_org",
  label = "Organization:",
  choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
  # selected = "Red Cross",
  selected = as.character(organization_data[1:4,][which(organization_data[1:4,2] == 1), 1]),
  width = "450px"
)

# Issue area
selectInput(
  "org1_issue", 
  label = "Issue Area:",
  choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
  # selected = "Emergency response",
  selected = ifelse(
    sum(organization_data[5:7,2]) == 0, "Emergency response",
    as.character(organization_data[5:7,][which(organization_data[5:7,2] == 1), 1])
  ),
  width = "450px"
)

@@

# Mediums to follow news
selectInput(
  "per1_news_medium",
  label = "Medium to follow news:",
  choices = c(
    "TV",
    "Print",
    "Online (not social media)",
    "Social media",
    "Radio",
    "Email newsletter",
    "News app"
  ),
  multiple = TRUE,
  # selected = c("TV", "Print", "Social media"),
  selected = deframe(persona_data[6:12,][which(persona_data[6:12,2] == 1), 1]),
  width = "450px"
)

@@

downloadHandler(
  filename = function() {
    paste0("org_data_",Sys.time(),".csv")
  },
  content = function(file) {
    write_csv(org_reactive(), file)
  }
)

@@

downloadHandler(
  filename = function() {
    paste0("persona_data_",Sys.time(),".csv")
  },
  content = function(file) {
    write_csv(per_reactive(), file)
  }
)

@@

### Imports

```{r import}
# Render the organization configurations as a table
renderTable({
  org_import = read_csv(input$file_org$datapath)

  org_import
})

# Render the persona configurations as a table
renderTable({
  per_import = read_csv(input$file_per$datapath)

  per_import
})

# Conditional argument to run IF new data is imported
# organization_data <- file_org
# persona_data <- file_per
```
